---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Almalki

<!-- badges: start -->
<!-- badges: end -->

The goal of Almalki is to ...

## Installation


And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("amwajg/ComputingStatistics")
```
## Example

This is a basic example which shows you how to solve a common problem:




## Idea primary aim

Health outcome measures can be used to measure health policies of various countries. Governments have the ability to enact polices that will improve health outcomes.This app will provide a way to measure the association between these policies and improvement in health outcomes.

The world data bank (WDB) contains information on health outcomes as well as other country level properties that can be influence by health policy. For my project, I found the relevant data series on the WDB and present this data to the user. The user will be able to explore these data series to find relations between policy actions and health outcome improvement. This interface will be coded in a RShiny gadget. With this app policy makers will be able to make data driven decisions. It is also possible for the user to
use their data instead of the data set in my package

## How to use the gadget

The input to the gadget is data generated by the WDI app
from data downloaded from the web site.

There is data set in the app called `h`. It would be possible for the user to provide their own data, but some more works need to be done by the user to create the option list. 

The app produced a density curve of the selected series. This is useful for evaluating the distribution of the series values. 


```{r example, eval=FALSE}
library(Almalki)
## basic example code
h %>% gadget_plot()
```


